Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
Update snippets

In our example, if one wanted to transform the inputs \texttt{X} before
fitting the logistic regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{center}
\texttt{X = StandardScaler().fit(X).transform(X)}
\end{center}

@@

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train} (through a
\texttt{FeatureUninon}), selecting the best of those features and then feeding
them to a linear model:
\begin{verbatim}
Pipeline([("pca", FeatureUnion([('linear_pca', PCA()),
                                ('kernel_pca', KernelPCA())])),
          ("feature_selection", SelectKBest()),
          ("linear_model", LinearRegression())
]).fit(X_train, y_train).predict(X_test)
\end{verbatim}

>>>>

In our example, if one wanted to transform the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{center}
\texttt{X\_train = StandardScaler().fit(X\_train).transform(X\_train)}
\end{center}

@@

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train} (through a
\texttt{FeatureUninon}), selecting the best of those features and then feeding
them to a logistic regression model:
\begin{verbatim}
Pipeline([("pca", FeatureUnion([('linear_pca', PCA()),
                                ('kernel_pca', KernelPCA())])),
          ("feature_selection", SelectKBest()),
          ("logistic_model", LogisticRegression())
]).fit(X_train, y_train).predict(X_test)
\end{verbatim}
